\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-06 cfhtlens.tex
cfhtlens.tex: Added JHD update

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio. For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins. The size of the pre-term $ [(\ell(\ell+1))^2]/(\ell+ 0.5)^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).

>>>>

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} discuss how corrections to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that the CMB lensing - galaxy lensing cross-correlation should include a pre-term $ [\ell(\ell+1)]^2/(\ell+ 0.5)^4$.   We have verified that this term would have negligible impact on current measurements, given the relatively low signal to noise ratio.  For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$.  The size of the pre-term, averaged over this range, is of the order of 0.01\%. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%). The pre-term reaches 1\% only for $\ell < 7$, which will become relevant for very large upcoming surveys but is negligible for current surveys.
